An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-04 indicators/paper/paper.tex
Update DV backfill claims
The original DV backfill numbers were calculated with code that called
covidcast_signal() repeatedly with different lag arguments. However,
specifying lag = k selects *only* those values issued exactly k days
after their time_value, meaning this only selects those values reissued
at a specific lag. If an estimate was reported once and never reissued,
it would not be included in this calculation, because it would only be
reported at one lag.

The new code uses as_of to get all estimates as of a specific lag, and
avoids this problem. This results in lower median backfil

Claims-based signals typically undergo heavy backfill as additional claims are
processed and errors are corrected; the median relative error between initial
reports and final values is over 20\% for such data, and only after roughly 35
days do estimates typically match finalized values within 5\%. However, the
systematic nature of this backfill, as illustrated in Figure~\ref{fig:dv_as_of},
suggests that statistical models could be fit (potentially separately for each
location) to estimate the final values from preliminary reports.

>>>>

Claims-based signals typically undergo heavy backfill as additional claims are
processed and errors are corrected; the median relative error between initial
reports and final values is over 10\% for such data, and only after roughly 30
days do estimates typically match finalized values within 5\%. However, the
systematic nature of this backfill, as illustrated in Figure~\ref{fig:dv_as_of},
suggests that statistical models could be fit (potentially separately for each
location) to estimate the final values from preliminary reports.
